Coherent Hyper-Raman Four Wave Mixing Vibrational Spectroscopy

### 2024-07-15 paper.tex
started2dplot

To explicitly incorporate vibronic coupling into the selection reules for DR-HDFG, we consider

>>>>

The impact of vibronic coupling in the 2D spectrum is made clear by using a simple model.
Using a two-well system described by $H_g = p^2/2m + 1/2 \hbar \omega q^2$ and $H_e = p^2/2m + 1/2 \hbar \omega (q-\Delta)^2$, the A and B contributions can be easily evaluated using Franck-Condon type integrals tabulated elsewhere. \cite{Carlson1988thesis}
